Current and future constraints on primordial magnetic fields

### 2017-01-31 pmf.tex
Added description of plasma instabilities...
as an alternative to loss of GeV flux, as an alternative to pmfs.

Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}, although there are alternative explanations \citep{broderick12}. 
High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}.

>>>>

Magnetic fields are ubiquitous in astronomy and are found almost universally in collapsed objects from stars to galaxies and galaxy clusters \citep[for a review, see][]{ryu12, widrow12}. 
There is even some evidence for magnetic fields in intergalactic space from \fermilat{} data \citep{neronov10}.
High energy $\gamma$-rays from blazars should  produce electron-positron pairs when the $\gamma$-rays collide with IR or optical photons. 
These pairs should later annihilate in at GeV energies, but the expected GeV flux is missing in the \fermilat{} observations. 
The missing flux could be explained by the deflection of particles due to intergalactic magnetic fields. 
If this is indeed the case then the GeV results set lower limits on the intergalactic magnetic field strength of $10^{-9} - 10^{-6}$\,nG \citep{tavecchio10,taylor11,dermer11,vovk12}. There are, however, alternative explanations involving plasma instabilities which may result in positron-electron pairs instead depositing their energy into the IGM as heat \citep{broderick12}.
